Global patterns of forest autotrophic carbon fluxes

### 2020-02-29 manuscript/manuscript draft.Rmd
worked on methods

Monthly data for PET, precipitation, and temperature was downloaded from the Climate Research Unit (CRU) time-series dataset v 4.03 [@harris_updated_2014], and for solar radiation from WorldClim2 [@fick_worldclim_2017], and used to calculate mean monthly PET, precipitation, temperature and solar radiation during the growing season. Total growing season precipitation and solar radiation were also calculated.

>>>>

Monthly data for PET, precipitation, and temperature from the CRU dataset v 4.03 [@harris_updated_2014], and solar radiation from WorldClim2 [@fick_worldclim_2017] were used to calculate mean monthly PET, precipitation, temperature and solar radiation during the growing season. Total growing season precipitation and solar radiation were also calculated.
